tables

### 2021-10-05 tables.Rmd
as

```{r}
tables %>%
  mutate_if(is.double, ~round(.,2)) |> 
  gt() %>% 
  gt_theme_espn() |> 
  tab_spanner(
    label = "Bayes Factor",
    columns = c(`14 DAT`:Yield)) |> 
    tab_footnote(
      footnote = "DAT, Days After Treatment - Waterhemp control",
      locations = cells_column_labels(
      columns = c(`14 DAT`,`28 DAT`)
    )) |> 
  gt_highlight_rows(rows = c(1,3:5,7), 
                    font_weight = "bold", 
                    fill = "#f8ff00")  -> fig_tab#|> 
#  gt_hulk_col_numeric(`14 DAT`:Yield, reverse = FALSE, trim = TRUE)

>>>>

```{r}
tables %>%
  mutate_if(is.double, ~round(.,2)) |> 
#  mutate(Parameter = fct_recode(Parameter,
#                                "glufosinate vs glufosinate + <i>S</i>-metolachlor" = "glufosinate vs glufosinate + S-metolachlor")) |> 
  gt() %>% 
  gt_theme_espn() |> 
  tab_spanner(
    label = "Bayes Factor",
    columns = c(`14 DAT`:Yield)) |> 
    tab_footnote(
      footnote = "DAT, Days After Treatment - Waterhemp control",
      locations = cells_column_labels(
      columns = c(`14 DAT`,`28 DAT`)
    )) |> 
  gt_highlight_rows(rows = c(1,3:5,7), 
                    font_weight = "bold", 
                    fill = "beige")  -> fig_tab#|> 
#  gt_hulk_col_numeric(`14 DAT`:Yield, reverse = FALSE, trim = TRUE)
